An open source scientific article about extrasolar magma oceans

### 2022-07-29 src/tex/ms.tex
make showyourwork find the static figure
add blindtext just to please Latex
add section headings

% Main body
\section{Introduction}
%\Blindtext[4]

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{../static/flowchart}
        \caption{Workflow of our hypothesis testing with Bioverse. In the first block, a stellar sample is generated based on XXX. The stars are then populated with planetary systems from XXX, to which a population-level trend can be applied. The planets' respective transit probabilities are computed. The second block simulates the exoplanet survey whereby selection effects and detection biases are introduced. Finally, the third block deals with testing a hypothesis based on the data from the simulated survey. By iterating through these steps, we compute the statistical power of testing the hypothesis given the assumed survey design.}
        \label{fig:flowchart}
    \end{centering}
\end{figure*}

@@

\section{The XXX Hypothesis}

>>>>

% Main body
\section{Introduction}
\Blindtext[4]

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/flowchart.pdf}
        \caption{Workflow of our hypothesis testing with Bioverse. In the first block, a stellar sample is generated based on XXX. The stars are then populated with planetary systems from XXX, to which a population-level trend can be applied. The planets' respective transit probabilities are computed. The second block simulates the exoplanet survey whereby selection effects and detection biases are introduced. Finally, the third block deals with testing a hypothesis based on the data from the simulated survey. By iterating through these steps, we compute the statistical power of testing the hypothesis given the assumed survey design.}
        \label{fig:flowchart}
    \end{centering}
\end{figure*}

@@

\section{The magma ocean hypothesis}

\subsection{Global magma oceans}
\todo[inline]{introduce magma oceans and their influence on planetary radii~\citep{Dorn2021}.\\ Might also be already fully covered in the Introduction section}

\subsection{Demographic imprint of magma oceans}
\todo{describe the expected imprint on the exoplanet population. \\Provide parametrizations from \citet{Dorn2021}'s models.}

\subsubsection{Parametrization}
\todo{specific parametrization, dependency on bulk planet/orbit params (doesn't have to be its own subsubsection)}

\begin{note}
The power from the host star per unit area at the position of a planet or stellar insolation $S$ in units of Earth's insolation is given by
    \begin{equation}
        \frac{S}{S_\oplus} = \left(\frac{L_\star}{L_\odot}\right) \left(\frac{au}{a}\right)^2 .
    \end{equation}

We further define the solar-equivalent semi-major axis $a_{eff} = a (L_\star/L_\odot)^{-1/2}$, at which a planet experiences the same insolation as a Solar System planet at an orbital distance $a$.
\end{note}

\subsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
